---
output: rmarkdown::github_document
---

# cfhttr

Workaround Cloudflare Anti-DDoS Protection

## Description

Some sites use Cloudflare's anti-DDoS protection to, well, avoid being DDoS'd.

However, many of these sites also host files that they intended for automated download workflows and often forget to exclude those from the heavy-handed anti-DDoS, javascript + human-required settings.

Cloudflare employs a few different anti-DDoS protection schemes. One involves a 503 HTTP response followed by the submission of a "challenge" that was solved via a bit of javascript on the page. _That's what this pacakge handles._ If you encounter other Cloudflare anti-DDoS protection schemes (especially the captcha one), then this won't work.

## NOTE

If this ceases to work it likely means that Cloudflare changed the challenge code. Please [file an issue](https://github.com/hrbrmstr/cfhttr/issues) so I can redo the workaround.

## What's Inside The Tin

The following functions are implemented:

- `cf_GET`: Cloudflare bypass version of `httr::GET()`

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/cfhttr")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(cfhttr)

# current verison
packageVersion("cfhttr")
```

```{r}
res <- cf_GET("https://www.bitmarket.pl/graphs/BTCPLN/90m.json")
str(httr::content(res, as="parsed"))
```
